---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rjd3x11plus: extended x11

<!-- badges: start -->
<!-- badges: end -->


## Installation 

To get the current stable version (from the latest release):

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3toolkit@*release")
remotes::install_github("rjdemetra/rjd3x11plus@*release")
```

To get the current development version from GitHub:

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3x11plus")
```


## High frequency data

infra monthly data

## Trend cycle estimation


## Contributing

Any contribution is welcome and should be done through pull requests and/or issues.

## Licensing

The code of this project is licensed under the [European Union Public Licence (EUPL)](https://joinup.ec.europa.eu/page/eupl-text-11-12).
