---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rjd3x11plus: extended x11

<!-- badges: start -->
<!-- badges: end -->


## Installation 

Running rjd3 packages requires **Java 17 or higher**. How to set up such a configuration in R is explained [here](https://jdemetra-new-documentation.netlify.app/#Rconfig) 


### Latest release

To get the current stable version (from the latest release):

- From GitHub:

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdverse/rjd3toolkit@*release")
remotes::install_github("rjdverse/rjd3x11plus@*release")
```

- From [r-universe](https://rjdverse.r-universe.dev/rjd3x11plus):

```{r, echo = TRUE, eval = FALSE}
install.packages("rjd3x11plus", repos = c("https://rjdverse.r-universe.dev", "https://cloud.r-project.org"))
```

### Development version

You can install the development version of **rjd3x11plus** from [GitHub](https://github.com/) with:

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdverse/rjd3x11plus")
```


## High frequency data

infra monthly data

## Trend cycle estimation


## Package Maintenance and contributing

Any contribution is welcome and should be done through pull requests and/or issues.
pull requests should include **updated tests** and **updated documentation**. If functionality is changed, docstrings should be added or updated.


## Licensing

The code of this project is licensed under the [European Union Public Licence (EUPL)](https://joinup.ec.europa.eu/collection/eupl/eupl-text-eupl-12).
